An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2011-08-03 Paper.tex
Submitted abstract to the MEG conference

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url}
\usepackage[sort,round]{natbib}
\usepackage[margin=1in]{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\frenchspacing
\onehalfspacing

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{E}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\ols}{\textsc{ols}}

@@

\author{Gray Calhoun}
\title{A comment on ``Approximately normal tests for equal predictive
  accuracy in nested models''}
\date{\today}
\maketitle

\begin{abstract} 
  \noindent This paper proposes a slight modification of
  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
  to estimate the alternative model under a fixed-length rolling
  window, but estimate the benchmark model under a recursive
  window. The resulting statistic gives an asymptotically normal test
  statistic that the benchmark model is correctly specified, even when
  it is nested in the alternative.  Moreover, the alternative model
  can be estimated using populare model selection methods, such as the
  \aic\ or \bic.

@@

\noindent Keywords: Out-of-Sample

@@

\noindent JEL Classification Numbers:

@@

\newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
an out-of-sample test of the null hypothesis that a small benchmark
model is correctly specified.  Their test compares the forecasting
performance of a pair of nested models, and the null hypothesis is
that the innovations in the smaller model are a martingale difference
sequence.  This test procedure is quite popular,\footnote{As of 19
  April 2011, \citet{ClW:06} has been cited by 25 papers indexed by
  the ISI Web of Knowledge, and \citet{ClW:07} by 35.} and one assumes
that this is due in part to the statistic's convenience.  The
statistic is approximately normal after adjusting for the estimation
error of the larger model.  Normality comes from a fixed-length
rolling window, as in \citet{GiW:06}, and the adjustment centers the
statistic at the appropriate population quantities.  This statistic is
especially convenient because other tests for similar hypotheses
\citep[see][among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01}
lead to a nonstandard limit distribution and place restrictions on the
models under consideration, while other asymptotically normal
statistics \citep{GiW:06} test a different null hypothesis.

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present monte carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal when the benchmark model is a random walk
\citep{ClW:06}. Estimating the parameters of the smaller model
invalidates the proof.

In this note, I prove that a slightly modified version of their
statistic is asymptotically normal even when the smaller model is
estimated.  Essentially, we need a consistent estimate of the forecast
errors of the pseudo-true version of the benchmark models, while
maintaining inconsistent estimates of the larger model's errors so
that we can ignore the fact that the models are nested.  We can meet
both needs by using different window strategies for each model.  We
estimate the benchmark model using a recursive window scheme, and
estimate the alternative using a fixed-length rolling window.

Mixing window strategies is uncommon but it shouldn't be. In most
applications, the null hypothesis imposes both equal accuracy between
the two models and stability.  The benchmark model rarely allows for
breaks, parameter drift, or other instability,\footnote{An exception
  might be \possessivecite{StW:08} IMA(1,1) model of inflation.} but
the researcher is typically concerned about instability.  Indeed,
concern about instability is often given as a reason for doing an
out-of-sample analysis, especially with a short rolling window
\citep{GiW:06,GiR:09,GiR:10}.  So using a different window strategy
for each model--a recursive window for the model that imposes
stability, and a rolling window for the model that relaxes
stability--is a natural approach and is similar in spirit to the
Likelihood Ratio Test\footnote{Using a rolling window for both models
  would be analagous to a Wald test and using recursive window for
  both would be like the LM test.}

Our statistic has a substantial advantage over existing out-of-sample
statistics for nested models: the benchmark can be essentially
arbitrary, as long as it obeys the necessary moment conditions.  In
particular, it can use model selection techniques like the \aic\ or
\bic\ to determine things like the number of lags to include, the
particular exogenous variables to include, etc.  Other methods that
test a similar hypothesis are unable to handle these models
\citep[except][which does not allow the benchmark to be
estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
both the alternative and the benchmark, but they test a different
aspect of forecasting performance.

We'll present our results as a single theorem.  The conditions are
essentially the same as
\citet{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a modified
window scheme.  We require that the benchmark model be estimated by
least squares, but that is for convenience and could be relaxed.
Changing the estimation strategy of the benchmark model would amount
to changing the null hypothesis.

\begin{thm}\label{thm:1}
  Suppose that the following hold:
  \begin{enumerate}
  \item The coefficients for the benchmark forecast,
    $\hat{y}_{1,t}(\beta_1)$, are estimated with least-squares over a
    recursive window:
    \[\hat{\beta}_{1t} = \argmin_{\beta} \sum_{s=1}^{t} (y_t -
    \hat{y}_{1t}(\beta))^2, \qquad t = R,\dots,T-1.\]
  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
    a rolling window of fixed length $R$: $\hat{y}_{2,t} \in
    \sigma(y_{t-R+1},\dots,y_t)$
  \item $z_t \equiv (y_t, \hat{y}_{1,t}(\beta_1^{*}), \hat{y}_{2t})$
    is strong mixing of size $-r/(r-2)$ and has uniformly bounded
    $r+\delta$ moments for some positive $\delta$, with $\beta^{*} =
    \argmin_{\beta} \E (y_t - \hat{y}_{1t}(\beta))^2$.

  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
  martingale difference sequence, $\sqrt{P} \bar f / \hat{\sigma}
  \to^d N(0,1)$, where
  \begin{align*}
  \bar f
  &\equiv P^{-1} \sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}),&  \hat{\sigma} &\equiv \Big(P^{-1}
  \sum_{t=R+1}^T (f_t(\hat{\beta}_{t-1}) - \bar f)^2\Big)^{1/2},
  \end{align*}
 and    
  \begin{equation*}
    f_t(\hat{\beta}_{t-1}) \equiv (y_t - \hat{y}_{1t}(\hat{\beta}_{t-1}))^2
    - (y_t - \hat{y}_{2t})^2 +
    (\hat{y}_{1t}(\hat{\beta}_{1,t-1}) - \hat{y}_{2t})^2
  \end{equation*}
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy $\tilde{R}_T \to \infty$ and
  $\tilde{R}_T/T \to 0$ and define $\tilde{P} = T - \tilde{R}$ Then
  \begin{equation*}
    P^{-1/2}\sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}) = \tilde{P}^{-1/2}
    \sum_{t=\tilde{R}+1}^T f_t(\hat{\beta}_{t-1}) + o_p(T^{-1/2}).
  \end{equation*}
  Now, $\hat{\beta}_t = B(t) H(t)$ with
  \begin{gather*}
    B(t) = \Big(t^{-1} \sum_{s=1}^t \Big\{\Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)
    \Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)' - (y_t -
    \hat{y}_{1t}(\bar{\beta}_t))\frac{\partial^2}{\partial\beta \partial\beta'}
    \hat{y}_{1t}(\bar{\beta}_t)\Big\}\Big)^{-1}, \\
    H(t) = t^{-1} \sum_{s=1}^t (y_t - \hat{y}_{1t}(\beta^{*}))
    \dd{\beta} \hat{y}_{1t}(\beta^{*}),
  \end{gather*}
  where $\bar{\beta}_t$ is between $\beta^{*}$ and $\hat{\beta}_t$
  element-by-element.  Then our new out-of-sample average satisfies
  the conditions of \citet[Theorem 4.1]{Wes:96} (with the moment and
  weak dependence conditions weakened as in \citet[Theorem
  2.3.1]{Mcc:00}).
\end{proof}

\input{mc}

\bibliography{AllRefs}

\end{document}

>>>>

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx}
\usepackage[sort,round]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\onehalfspacing

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lema}{Lemma}[section]
\newtheorem{alg}{Algorithm}
\newtheorem{asmp}{Assumption}[section]

\theoremstyle{definition}

\newtheorem{example}{Example}
\newtheorem{defn}{Definition}
\newtheorem{rem}{Remark}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}
%\DeclareMathOperator{\vec}{vec}
\DeclareMathOperator{\vech}{vech}

\DeclareMathOperator{\pr}{Pr}

\newcommand{\X}{\ensuremath{\mathrm{X}}}
\newcommand{\R}{\ensuremath{\mathrm{R}}}
\newcommand{\p}{\ensuremath{\mathrm{P}}}

\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\ned}{\textsc{ned}}
\newcommand{\clt}{\textsc{clt}}
\newcommand{\fclt}{\textsc{fclt}}
\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\ols}{\textsc{ols}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\oos}{\textsc{oos}}
\newcommand{\gdp}{\textsc{gdp}}
\newcommand{\hac}{\textsc{hac}}
\newcommand{\fwe}{\textsc{fwe}}
\newcommand{\cdf}{\textsc{cdf}}
\newcommand{\ma}{\textsc{ma}}

\renewcommand{\Re}{\ensuremath{\mathbb{R}}}

@@

\author{Gray
  Calhoun\thanks{\texttt{http://www.econ.iastate.edu/$\sim$gcalhoun};
    Economics Department; Iowa State University; Ames, IA 50011.
    Telephone: (515) 294-6271.  Email: \texttt{gcalhoun@iastate.edu}.}
  \\ Iowa State University}

\title{An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models} \date{\today}
\maketitle

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
      Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  popular model selection methods, such as the \aic\ or \bic.  This
  paper also presents a new bootstrap procedure based on
  \citet[\textit{Econometrica}]{RoW:05} to compare multiple models
  while controlling family-wise error that substantially improves
  existing block bootstrap methods for out-of-sample statistics.  This
  procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\noindent Keywords: Forecast Evaluation, Martingale Difference
Sequence, Model Selection, Family-Wise Error Rate; Multiple Testing;
Bootstrap; Reality Check

@@

\noindent JEL Classification Numbers: C22, C53

@@

\newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
an out-of-sample (\oos) test of the null hypothesis that a small
benchmark model is correctly specified.  Their test compares the
forecasting performance of a pair of nested models, and the null
hypothesis is that the innovations in the smaller model form a
martingale difference sequence.  This test procedure is
popular,\footnote{As of 03 June 2011, \citet{ClW:06} has been cited by
  26 papers indexed by the \textsc{isi} Web of Knowledge, and
  \citet{ClW:07} by 37. They have been cited by 113 and 165 papers
  respectively indexed by Google Scholar.} and one assumes that this
is due in part to the statistic's convenience.  The statistic is
approximately normal after adjusting for the estimation error of the
larger model.  Normality comes from a fixed-length rolling window, as
in \citet{GiW:06}, and the adjustment centers the statistic
appropriately.  This statistic is especially convenient because other
tests for similar hypotheses \citep[among
  others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
nonstandard limit distribution and place restrictions on the models
under consideration, while other asymptotically normal statistics test
a different null hypothesis \citep{GiW:06} or place assumptions on the
models and \dgp\ that are rarely appropriate in empirical work
\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal when the benchmark model is a random walk
\citep{ClW:06}. Estimating the parameters of the smaller model
invalidates their proof.

In this paper, I show that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, we need a consistent estimate of the pseudo-true
benchmark model, while maintaining an inconsistent estimate of the
larger model so that we can ignore nesting.  We can meet both needs by
using different window strategies for each model; the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes both equal accuracy between
the two models and stability.  The benchmark model rarely allows for
breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed in \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; both approaches should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a likelihood ratio
test instead of an \textsc{lm} or Wald test.

This statistic has a substantial advantage over existing \oos\
statistics for nested models: the alternative can be essentially
arbitrary, as long as it obeys the necessary moment conditions.  In
particular, researchers can use model selection techniques like the
\aic\ or \bic\ to determine the number of lags to include, the
particular exogenous variables to include, etc.  Other methods that
test a similar hypothesis are unable to handle these models
\citep[except][which does not allow the benchmark to be
estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
both the alternative and the benchmark but, as mentioned earlier, they
test a different aspect of forecasting performance.

This paper focuses on nested models, as they have received the most
attention in the empirical and theoretical literature, but the
statistic can be used with non-nested models as well.  This generality
is useful, since \citepos{Wes:96} results do not apply to non-nested
models if they both encompass the true \dgp, which is allowable under
the null: in the limit, both models will converge to the \dgp\ and
give identical forecasts.  Consequently, the naive \oos\ $t$-test is
invalid, even after correcting the standard error to reflect parameter
uncertainty.  Constructing an \oos\ test for non-nested models using
\citepos{ClM:01} approach would be difficult.  To my knowledge, this
paper gives the first \oos\ test of equal predictive ability for
non-nested models that does not implicitly rule out both models
encompassing the \dgp.\footnote{Again, \citet{GiW:06} does not make
  this implicit assumption, but their statistic tests a different null
  hypothesis.}

Statistics for comparing two models are useful, but a researcher often
has a set of potential models, and wants to know which of them
significantly outperform the benchmark.  As \citet{Whi:00} shows,
looking at the naive $p$-values is misleading, but bootstrapping the
statistics can lead to a valid test (White calls this procedure the
``bootstrap reality check'').  So I present a test for equal
predictive ability of multiple models based on \citepos{RoW:05} StepM,
which uses a step-down procedure that iteratively rejects models to
achieve higher power than the reality check (see Theorem~\ref{res:2}
for details) and will indicate which of the models improves on the
benchmark.

I also present a new result for the validity of using the stationary
boostrap with \oos\ statistics, which is necessary to verify that the
StepM is appropriate.  Existing results on boostrapping
\oos\ statistics have some drawbacks.  \citet{Whi:00} and
\citet{Han:05} use the stationary bootstrap, but require the test
sample to be much smaller than the training sample, which is obviously
inappropriate here.  \citet{CoS:07} relax that requirement, but only
consider the moving block bootstrap \citep{LiS:92,Kun:89} and make the
statistic more complicated than necessary by adjusting the objective
function of the bootstrapped statistic to center it
correctly.\footnote{Their recentering is required for consistency and
  does not give higher order accuracy.}  A parametric bootstrap, such
as that used by \citet{ClM:11}, would be difficult to implement here
since we want to test whether several different null hypotheses hold
individually (as I'll discuss later, Clark and McCracken test a single
null hypothesis that describes the behavior of all of the models under
consideration and does not let the researcher know which of the models
outperforms, only that at least one does).  So this paper's result for
the stationary bootstrap of \oos\ statistics considerably improves on
existing procedures.

The next section presents our theoretical result and
Section~\ref{sec:2} presents two simulations that compare our pairwise
\oos\ test to \poscw\ original statistic.  Section~\ref{sec:3}
demonstrates the use of our statistic by reanalyzing \citepos{GoW:08}
study of excess return predictability. Section~\ref{sec:4} concludes.

\section{Theoretical Results}\label{sec:1}
The first result modifies \citepos{ClW:07} so that it is
asymptotically normal. The conditions are essentially the same in
existing papers
\citep[e.g.][]{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a
modified window scheme.  Our result follows from \citet{Wes:96},
treating the alternative model's forecasts as additional data. Note
that asymptotic equivalence does not hold so we need to account for
parameter estimation error.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    \begin{equation}
      \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
      \sum_{s=2}^t x_{t-1} y_t, \qquad t = R,\dots,T.
    \end{equation}
    Also define $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1}
    x_{t-1}'\big)^{-1} \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-1/2$ on a strong mixing series of size $-r/(r-2)$ for $r>2$ or a
    uniform mixing series of size $-r/2(r-1)$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = P^{-1} \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    P^{-1} \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$, $\sqrt{P} \bar f /
  \hat{\sigma} \to^d N(0,1)$, where
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \frac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \frac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - (R/P) \log(1 + P/R)$, $\bar{g} = T^{-1}
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
  g_t(\beta) = \Bigg\{\frac{2}{P}\sum_{t=R}^{T-1} x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Bigg\} \big(\X'\X / T \big)^{-1}  x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

The following remarks are relevant to Theorem~\ref{res:1}:

\begin{rem}
  Forecasters will almost always be interested in the one-sided
  alternative that $\E f_t(\beta_0) > 0$; i.e. that the alternative
  model is expected to forecast better than the benchmark.
\end{rem}

\begin{rem}
  These results are presented for one-period-ahead forecasting for
  simplicity.  They can be extended to forecasting at a longer horizon
  by appropriately modifying the variance-covariance matrix to account
  for the correlation structure of the forecast errors. (i.e. for
  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
\end{rem}

\begin{rem}
  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

\begin{rem}
  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
  fixed.  But using West's general formula for $\Pi$ (which holds when
  $P/R$ converges as $T \to \infty$) can improve the statistic in
  practice, since researchers often invoke ``fixed $R$'' asymptotics
  when $R$ is large.  Section~\ref{sec:2} shows via Monte Carlo that
  this approximation can be accurate even when $R$ and $P$ are equal.
\end{rem}

\begin{rem}
  If one wants to test the less restrictive null hypothesis that
  $y_{t1} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with \hac\
  counterparts.  Lemma~\ref{res:a5} presents a more general version of
  the theorem that can cover this case.
\end{rem}

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This may not be appropriate,
  depending on the loss function or utility function of interest.  Our
  statistic can be modified to test implications of optimal forecasts
  under other loss functions \citep[see][]{PaT:07,PaT:07b}.  Again,
  Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

I also use Lemma~\ref{res:1} to test multiple models at once.  There
are two approaches one can take.  The first is to test whether any of
the models can improve on the benchmark; \citet{Whi:00},
\citet{Han:05}, and \citet{ClM:11} take this approach.  This approach
requires testing a single null hypothesis, that the best model is no
better than the benchmark, and one wants a test statistic to control
size as usual.  The second approach, taken by \citet{RoW:05}, is to
try to determine which models outperform the benchmark, and to find as
many as possible that do.  Now there are as many hypotheses as there
are models, so we need to control a quantity similar to size, the
family-wise error rate, which is the probability that one or more true
hypotheses is rejected.  To appreciate the difference between these
two approaches, suppose that there are two models and the first
outperforms a benchmark but the second doesn't.  Under the first
approach, finding that both models outperform the benchmark is fine:
the null (that none of them do) is false so we want to reject.  But
under the second approach, this finding is a failure, as we
incorrectly believe that the second model beats the benchmark.

While methods like \citepos{Whi:00} and \citepos{Han:05} control the
family-wise error, \citepos{RoW:05} StepM procedure will typically find
more outperforming models while still controlling the family-wise error
rate.  All of these methods rely on the bootstrap to estimate the
joint dependence between the test statistic associated with each
model.  The bootstrap we will use in this paper is new, and is
outlined in Algorithm~\ref{alg:1}.
\begin{alg}\label{alg:1}
  \begin{enumerate}
  \item Define the data matrices $\X_\R = (X_1,\dots,X_R)'$ and $\X_{\p} =
    (X_{R+1},\dots,X_{T-1})$ with
    \begin{equation*}
      X_t = \begin{cases}
        (y_{t+1}, x_t')' & t \leq R \\
        (y_{t+1}, x_t', \hat{y}_{1,t+1})' & t > R.
      \end{cases}
    \end{equation*}
  \item Draw $B$ samples of $P$ observations from $\X_{\p}$ using the
    stationary bootstrap with expected block size $b$ and denote each
    sample as $\X_{\p, l}^{*}$; let $\X_l^{*} = [\X_{\R}', \X_{\p,l}^{*\prime}]'$.
  \item Estimate $\bar{f}^{*}_l$ and $\hat{\sigma}_l^{*}$ as in
    Theorem~\ref{res:1} for each bootstrap sample $\X^{*}_l$.
  \end{enumerate}
\end{alg}

Theorem~\ref{res:2} details the final procedure.

\begin{thm}\label{res:2}
  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
  on the alternative model, $\hat{y}_{1t}$, holding for each of the
  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$, let the subscript
  $l$ denote the different quantities associated with $\hat{y}_{lt}$
  (i.e. $\mathcal{F}_{lt}$, etc.), and let $H_l$ be the null
  hypothesis that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
  $F_{lt}$.  Also assume that the long-run variance-covariance matrix
  of the vector $(\bar{f}_1,\dots,\bar{f}_m)'$ is uniformly positive
  definite.

  Let the $*$-superscript denote a random variable with the
  distribution induced by the stationary bootstrap of
  Algorithm~\ref{alg:1}, letting $X_t = (y_{t+1}, x_t', \hat{y}_{1,t+1},
  \dots, \hat{y}_{m, t+1})'$ for $t > R$ (and unchanged for $t \leq
  R$).  Define $M_j$ as follows:
  \begin{enumerate}
  \item define $M_0 = \emptyset$,
  \item for $j = 1,2,\dots,m$, let $M_j = \{i : \bar{f}_{i} /
    \hat{\sigma}_i > \hat{d}_j\}$, where $\hat{d}_j$ is the $1-\alpha$
    quantile of $\max_{i \notin M_{j-1}} (\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1})) / \hat{\sigma}_i^{*}$,
  \end{enumerate}
  and reject all of the hypotheses $H_i$ with $i \in \bigcup_{j=0}^m
  M_j$.

  If $b \to \infty$ and $b/P \to 0$, this algorithm controls the
  \fwe\ at level $\alpha$ for the family of null hypotheses $H_i$
  ($i=1,\dots,m$): the probability of rejecting any true $H_i$ is less
  than or equal to $\alpha$.  Moreover, the probability that $H_i$ is
  rejected converges to one if $y_{t} - \hat{y}_{0t}(\beta_0)$ and
  $\hat{y}_{it}$ have nonzero correlation.
\end{thm}

The following remarks apply to Theorem~\ref{res:2}.

\begin{rem}
  The bootstrap does not and should not exploit the \mds\ null
  hypotheses, even though the individual variance estimators do.
  Imposing this null hypothesis (potentially through a parametric
  bootstrap, as in \citen{ClM:11}) requires that $y_t - \hat{y}_{0t}$
  be an \mds\ with respect to the filtration \[\sigma((y_t, z_{1,t-1},
  \dots, z_{m,t-1}), (y_{t-1}, z_{1,t-2}, \dots, z_{m,t-2}), \dots)\]
  which is stronger than even the composite null that it is an \mds\
  with respect to all of the $m$ filtrations $\sigma(y_t, z_{i,t-1},
  y_{t-1}, z_{i,t-2}, \dots)$ for $i = 1,\dots,m$.  Using a bootstrap
  that imposes the null will give us a correct approximation to the
  marginal distribution of each test statistic individual test
  statistic, $\bar{f}_i / \hat{\sigma}_i$, but it will not necessarily
  get their joint distribution correct.
\end{rem}

\begin{rem}
  If calculating $\hat{\sigma}_i$ is burdensome, one can do the same
  bootstrap without studentizing the statistics.  This procedure is
  likely to have worse size and power properties, but may be more
  convenient.  One could also estimate the variance with a second
  bootstrap step, but execution might take too long to be practical
  See \citet{Han:05} and \citet[Section~4.2]{RoW:05} for a discussion
  of the benefits of studentization.
\end{rem}

\begin{rem}
  Since the distribution of $\bar{f}_i$ is affected by the error in
  estimating $\beta_0$, we need to re-estimate the benchmark model
  in each bootstrap sample, unlike \citet{Whi:00}, \citet{Han:05}, or
  \citet{HuW:10}.  But we do not need to re-estimate the alternative
  models, so the additional computational burden is relatively small.
\end{rem}

\begin{rem}
  How we handle the first $R$ observations does not affect the
  asymptotic properties since $R$ is finite.  I've chosen to put them
  at the beginning of each bootstrap sample so that sample means
  correspond to population means of the bootstrap distribution.  Note
  that the alternative forecasts are not defined for the first $R$
  observations, so running the stationary bootstrap over the full
  dataset is not possible.
\end{rem}

\begin{rem}
  See \citet{RoW:05,RoW:06} for guidance on block length
  selection.
\end{rem}

\begin{rem}
  If the number of alternative models is large, controlling the \fwe\
  may be too strict a criterion.  \citet{RSW:08} discuss procedures to
  control criteria other than the \fwe, and one can use their
  generalizations of the StepM procedure here as well.
\end{rem}

\section{General Results for the Bootstrap}\label{sec:1b}
The validity of the stationary boostrap in Theorem~\ref{res:2} is a
special case of a result of independent interest---the validity in
general of the stationary bootstrap when \oos\ statistics are
asymptotically normal.  Existing results---\citet{Whi:00},
\citet{Han:05}, and \citet{CoS:07}---are not appropriate here;
\citet{Whi:00} and \citet{Han:05} require that $R$ be very large,
while this paper requires $R$ to be finite; and \citet{CoS:07} require
a complicated modification of the statistic of interest be used to
create the bootstrap distribution.  Instead of using these results,
I'll present one more general.  The proof largely follows the approach
of \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}, using the
arguments of \citet{Cal:11d} for asymptotic normality.

In this section, let $\to^{p^{*}}$ and $\to^{d^{*}}$ refer to
convergence in probability or distribution conditional on the observed
data.  Similarly, $\E^{*}$, $\var^{*}$, and $\cov^{*}$ refer to the
expectation, variance, and covariance with respect to the probability
measure induced by the stationary bootstrap, and $y_t^{*}$, etc. is
the random variable $y_t$ but under the bootstrap-induced \cdf.

Note that the notation in this section is more general than that of
Section~\ref{sec:1}.  The assumptions required are generalizations of
the conditions of Theorems~\ref{res:1} and~\ref{res:2}.  See
\citet{Wes:96,Wes:06}, \citet{WeM:98}, and \citet{Mcc:00} for a
discussion of these conditions, as theirs are nearly identical.

\begin{asmp}\label{asmp:a1} 
  Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-1/2$ on a
  strong mixing series $\{V_t\}$ of size $-r/(r-2)$, with $r > 2$.
\end{asmp}
